Partial rank data with the \pkg{hyper2} package: likelihood functions for generalized Bradley-Terry models

### 2019-05-03 inst/collusion_chess_draws.Rnw
more work

Figure~\ref{kka} suggests a number of interesting hypotheses.
Firstly, we observe that $p_D=0$ cannot possibly be the case: the
likelihood would be identically zero, owing to the nonzero term in the
numerator of the last term of Equation~\ref{likelihood_kka}.  However,
it is conceivable that $p_W=0$ and this hypothesis can readily be
tested using the concept of profile likelihood.

>>>>

Figure~\ref{kka} suggests a number of interesting hypotheses.
Firstly, we observe that $p_D=0$ cannot possibly be the case: the
likelihood would be identically zero, owing to the nonzero term in the
numerator of the last term of Equation~\ref{likelihood_kka}.  Indeed,
we can give a maximum likelihood estimate for the various strengths
using the \code{maxp()}``` functionality of the software:

<<>>=
maxp(karpov_kasparov_anand)
@

We see that $\widehat{p_D}\simeq 0.53$, compare the naive estimate of
$\frac{224}{365}\simeq 0.61$ given by observing 224 draws among 265
matches.  Secondly, we may make inferences about $p_W$.  It is
conceivable that $p_W=0$ as this term does not appear on its own in
the numerator of any term.  We may test $H_0\colon p_W=0$ using the
method of support.

<<>>=
small <- 1e-4

e <- function(white){
    maxp(
        karpov_kasparov_anand,
        startp=c(1/3-small,1/3-small,1/3-small,small),
        fcm=-cbind(0, 0, 0, 1),fcv= -white,give=TRUE)$value
}
e(0.001)
e(0.002)
e(0.003)
maxp(karpov_kasparov_anand,give=TRUE)$value
328.2975-335.6025
@

that is, well over 7 units of support, exceeding Edwards's
two-units-of-support per degree of freedom and we can reject $p_W=0$.

One very natural hypothesis would be $H_{A=K=K}\colon
p_\mathrm{Karpov}=p_\mathrm{Kasparov}=p_\mathrm{Anand}$.  This too is
readily testable:
